\documentclass[class=article, crop=false]{standalone}
\usepackage[subpreambles=true]{standalone}
\usepackage{import}
\usepackage{enumitem} % Format list spacing 

\begin{document}

\subsection{Whitepaper Version History}
The following is a complete version history of this whitepaper. Unless otherwise noted, references within this Whitepaper Version History are not updated to reflect later changes.

\begin{itemize}[topsep=0pt, itemsep=3pt,leftmargin=16pt]
    \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_0_0.pdf}{1.0.0} (August 6, 2021)
    \begin{itemize}
        \item Original whitepaper.
    \end{itemize}
    \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_0_1.pdf}{1.0.1} (August 10, 2021) [Code Version 1.0.1 should have been 1.0.0.]
    \begin{itemize}
        \item Updated \hyperlink{section.5}{Section 5} to reflect that the first \term{Season} began when the \code{init} function was called as part of the Beanstalk deployment.
        \item Updated \hyperlink{subsubsection.6.4.3}{Section 6.4.3} to reflect that the first \term{Season} began when the \code{init} function was called as part of the Beanstalk deployment, and state that $P_{\overline{t}} = 1$ for each \term{Season} that contains a \term{Pause}.
        \item Moved a paragraph from \hyperlink{subsubsection.6.4.3}{Section 6.4.3 to 6.4.4} for better flow.
        \item Updated the definition of $a^q$ in \hyperlink{subsubsection.6.4.5}{Section 6.4.5} to reflect the correct base commit award. [$a^q$ was defined correctly in Version 1.0.0 but defined incorrectly in Versions 1.0.1 - 1.1.2.]
        \item Updated \hyperlink{subsection.9.1}{Section 9.1} to reflect that the first \term{Season} began when the \code{init} function was called as part of the Beanstalk deployment.
    \end{itemize}
    \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_1_0.pdf}{1.1.0} (August 26, 2021)
    \begin{itemize}
        \item Updated \hyperlink{subsection.6.3}{Section 6.3} to reflect the new \term{Stalk} equations, as amended by \href{https://bean.money/bip-0}{BIP-0}.
        \item Added $t_f$ to the \hyperlink{subsection.14.11}{Glossary}.
    \end{itemize}
    \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_1_1.pdf}{1.1.1} (September 15, 2021)
    \begin{itemize}
        \item Added \href{https://bean.money/}{bean.money} URL to the cover page.
    \end{itemize}
    \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_1_2.pdf}{1.1.2} (September 23, 2021)
    \begin{itemize}
        \item Updated citation 16 with the correct URL for \href{https://bean.money/bip-0}{BIP-0}.
    \end{itemize}
    \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_1_3.pdf}{1.1.3} (October 15, 2021) [Whitepaper Version 1.1.3 should have been 1.2.0. Code Version 1.1.2 should have been 1.2.0.]
    \begin{itemize}
        \item Updated the definition of $a^q$ in \hyperlink{subsubsection.6.4.5}{Section 6.4.5} to reflect the correct base commit award. [$a^q$ was defined correctly in Version 1.0.0 but defined incorrectly in Versions 1.0.1 - 1.1.2.]
    \end{itemize}
    \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_3_0.pdf}{1.3.0} (November 11, 2021)
    \begin{itemize}
        \item Updated \hyperlink{subsubsection.8.4.8}{Section 8.4.8} to reflect the latest \term{Weather} changes, as amended by \href{https://bean.money/bip-2}{BIP-2}.\footnote{\href{https://bean.money/bip-2}{bean.money/bip-2}}
        \item Updated \hyperlink{section.11}{Section 11} to reflect an updated understanding of potential uses of Beanstalk. 
        \item Created an \hyperlink{section.14}{Appendix} and moved \hyperlink{subsection.12.1}{Section 12} and \hyperlink{subsection.12.2}{Section 13} to the \hyperlink{section.14}{Appendix} as \hyperlink{section.12}{Sections} \hyperlink{subsection.12.1}{12.1} and \hyperlink{subsection.12.2}{12.2}, respectively. 
        \item Updated \hyperlink{subsection.12.1}{Section 12.1} to reflect an updated understanding of potential uses of Beanstalk. 
        \item Added \hyperlink{subsection.12.3}{Section 12.3}, a Whitepaper Version History, to the \hyperlink{section.14}{Appendix}.
    \newpage
    \end{itemize}
    \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_3_1.pdf}{1.3.1} (December 3, 2021)
    \begin{itemize}
        \item Removed a sentence from the second paragraph of \hyperlink{subsection.6.2}{Section 6.2} to reflect the new \term{Stalk} equations, as amended by \href{https://snapshot.org/\#/beanstalkfarms.eth/proposal/0xffc6033eb5a4e53f4da5df1c4011bacc12244914885fe11e6a6f2d09d856feed}{Pause Patch-0}.
        \item Updated \hyperlink{subsection.6.3}{Section 6.3} to reflect the new \term{Stalk} equations, as amended by \href{https://snapshot.org/\#/beanstalkfarms.eth/proposal/0xffc6033eb5a4e53f4da5df1c4011bacc12244914885fe11e6a6f2d09d856feed}{Pause Patch-0}.
        \item Added a comma in the second paragraph of \hyperlink{subsection.8.3}{Section 8.3} for clarity.
        \item Added $f^{\bean}$ to the \hyperlink{subsection.14.11}{Glossary}. 
        \item Italicized \term{Stalk} in Whitepaper Version History changes for Version 1.1.0.
    \end{itemize}
    \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_4_0.pdf}{1.4.0} (December 10, 2021)
    \begin{itemize}
        \item Modified the formatting of two equations and the language of the fifth paragraph in \hyperlink{subsection.6.3}{Section 6.3} for clarity.
        \item Changed variables $b_h$, $h$ and $\Lambda_h$ to $b_{\Omega}$, $\Omega$ and $\Lambda_{\Omega}$, respectively, in \hyperlink{subsection.6.3}{Section 6.3} and the \hyperlink{subsection.14.11}{Glossary}.
        \item Updated Sections \hyperlink{subsection.7.1}{7.1}, \hyperlink{section.8}{8}, \hyperlink{subsection.8.1}{8.1}, \hyperlink{subsection.8.2}{8.2}, \hyperlink{subsection.8.3}{8.3} and \hyperlink{subsubsection.8.4.5}{8.4.5} to reflect the new \term{Soil} mechanism, as amended by \href{https://bean.money/bip-6}{BIP-6}.\footnote{\href{https://bean.money/bip-6}{bean.money/bip-6}}
        \item Added $h_t$ to the \hyperlink{subsection.14.11}{Glossary}. 
        \item Corrected a typo in the change history for Whitepaper Version \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_3_1.pdf}{1.3.1} in \hyperlink{subsection.12.3}{Section 12.3}.
    \end{itemize}
    \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_5_0.pdf}{1.5.0} (December 18, 2021)
    \begin{itemize}
        \item Modified the language of the seventh paragraph in \hyperlink{section.6.3}{Section 3} for clarity.
        \item Switched all $>$ to $<$ for consistency and clarity.
        \item Updated Sections \hyperlink{subsection.6.2}{6.2}, \hyperlink{subsection.6.3}{6.3} and \hyperlink{subsection.9.6}{9.6}, and \hyperref[fig 1]{Figure 1}, to reflect the new \term{Convert} mechanism, as amended by \href{https://bean.money/bip-7}{BIP-7}.\footnote{\href{https://bean.money/bip-7}{bean.money/bip-7}}
        \item Updated \hyperref[fig 2]{Figure 2} to mirror the new design of \hyperref[fig 1]{Figure 1}. 
        \item Modified the language of the second paragraph in \hyperlink{section.11}{Section 11} for consistency.
    \end{itemize}
    \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_6_0.pdf}{1.6.0} (January 12, 2022)
    \begin{itemize}
        \item Modified the last sentence of the \hyperlink{abstract}{Abstract} for better flow.
        \item Changed a semicolon to a colon in the fourth paragraph of \hyperlink{section.1}{Section 1} for clarity.
        \item Corrected a typo in the second paragraph of \hyperlink{section.3}{Section 3}.
        \item Updated the fourth and fifth paragraphs of \hyperlink{section.3}{Section 3} to reflect an updated understanding of potential uses of Beanstalk.
        \item Modified the language of the fifth paragraph of \hyperlink{section.4}{Section 4} for consistency.
        \item Modified the language of the first paragraph of \hyperlink{subsection.6.1}{Section 6.1} for clarity.
        \item Updated the first paragraph of \hyperlink{subsection.6.2}{Section 6.2} to reflect the new \term{Withdrawal} \term{Freeze}, as amended by \href{https://bean.money/bip-9}{BIP-9}.
        \item Modified the language of the second paragraph of \hyperlink{subsection.6.2}{Section 6.2} for clarity.
        \item Modified the language of the first, third and twelfth paragraphs of \hyperlink{subsection.6.3}{Section 6.3} for clarity.
        \item Modified the equation for $K_t$ for consistency.
        \item Modified the language of the first paragraph of \hyperlink{subsection.6.4}{Section 6.4} for clarity.
        \item Updated \hyperlink{subsubsection.6.4.1}{Section 6.4.1} to reflect the new governance policy, as amended by \href{https://bean.money/bip-9}{BIP-9}.
        \item Corrected a typo in the third paragraph of \hyperlink{subsubsection.6.4.2}{Section 6.4.2}.
        \item Changed variable $E_f$ to $E_{\Psi}$ in \hyperlink{subsubsection.6.4.3}{Section 6.4.3} and the \hyperlink{subsection.14.11}{Glossary}.
        \item Corrected typos in the first paragraph of \hyperlink{subsubsection.6.4.4}{Section 6.4.4} and the fourth paragraph of \hyperlink{subsubsection.6.4.5}{Section 6.4.5}.
        \item Modified the language of the third paragraph of \hyperlink{subsubsection.6.4.5}{Section 6.4.5} for clarity.
        \item Modified the language of the first paragraph of \hyperlink{section.7}{Section 7} for consistency.
        \item Updated the second paragraph of \hyperlink{subsection.7.2}{Section 7.2} to reflect the new \term{Soil} policy, as amended by \href{https://bean.money/bip-9}{BIP-9}.
        \item Updated \hyperlink{subsection.8.2}{Section 8.2} to reflect the new Bean supply policy, as amended by \href{https://bean.money/bip-9}{BIP-9}.
        \item Corrected a typo and modified the language for clarity in the penultimate paragraph of \hyperlink{subsection.8.2}{Section 8.2}.
        \item Modified the last equation in \hyperlink{subsection.8.2}{Section 8.2} for consistency.
        \item Updated \hyperlink{subsection.8.3}{Section 8.3} to reflect the new \term{Soil} supply policy, as amended by \href{https://bean.money/bip-9}{BIP-9}.
        \item Modified the language of the second paragraph of \hyperlink{subsection.8.3}{Section 8.3} for clarity.
        \item Updated the equation for $S_t^{\text{start}}$ in \hyperlink{subsection.8.3}{Section 8.3} to reflect the new \term{Soil} supply policy, as amended by \href{https://bean.money/bip-9}{BIP-9}.
        \item Corrected a typo in the first paragraph of \hyperlink{subsubsection.8.4.1}{Section 8.4.1}.
        \item Modified the language of the second paragraph of \hyperlink{subsubsection.8.4.3}{Section 8.4.3} for clarity.
        \item Modified the language of the first and second paragraphs of \hyperlink{subsubsection.8.4.4}{Section 8.4.4} for clarity.
        \item Updated \hyperlink{subsubsection.8.4.5}{Section 8.4.5} to reflect the new \term{Soil} supply policy, as amended by \href{https://bean.money/bip-9}{BIP-9}.
        \item Modified the language of the first paragraph of \hyperlink{subsubsection.8.4.7}{Section 8.4.7} for clarity.
        \item Corrected a typo, and modified the language to reflect the new \term{Season of Plenty} timer, as amended by \href{https://bean.money/bip-9}{BIP-9}, in the second paragraph of \hyperlink{subsection.8.2}{Section 8.2}.
        \item Modified the language of the third paragraph of \hyperlink{subsection.9.1}{Section 9.1} for clarity.
        \item Modified the section titles of Sections \hyperlink{subsection.9.1}{9.1}, \hyperlink{subsection.9.2}{9.2} and \hyperlink{subsection.9.4}{9.4} for consistency.
        \item Modified the language of the second and third paragraphs of \hyperlink{subsection.9.4}{Section 9.4} for clarity.
        \item Modified the language of the first and second paragraphs of \hyperlink{subsection.9.6}{Section 9.6} for clarity.
        \item Modified the language of the third and fourth paragraphs of \hyperlink{subsection.9.6}{Section 9.6} to reflect current incentive structures.
        \item Corrected a typo in the second paragraph of \hyperlink{section.10}{Section 10}.
        \item Modified the language of the fourth paragraph of \hyperlink{section.10}{Section 10} for accuracy.
        \item Updated the fifth paragraph of \hyperlink{section.11}{Section 11} to reflect an updated understanding of potential uses of Beanstalk. 
        \item Modified the section title, and language of the first paragraph, of \hyperlink{subsection.12.1}{Section 12.1} to clarify the listed parameters are current.
        \item Modified the conventions in \hyperlink{subsection.12.2}{Section 12.2} to reflect consistency with regard to Latin letters only.
        \item Added $K^{\text{min}}$, $\Lambda^{\text{Silo}}$, and $\xi$ to the \hyperlink{subsection.14.11}{Glossary}. 
        \item Changed $S_{t-1}^{\text{end}}$ to $S_t^{\text{end}}$ in the \hyperlink{subsection.14.11}{Glossary} for consistency. 
        \item Removed $B_t$, $S_t^{\text{max}}$, and $R_S^{\text{max}}$ from the \hyperlink{subsection.14.11}{Glossary}. 
        \item Modified the language in the change histories for Versions \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_0_1.pdf}{1.0.1}, \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_1_0.pdf}{1.1.0}, \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_1_3.pdf}{1.1.3}, \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_3_1.pdf}{1.3.1} in \hyperlink{subsection.12.3}{Section 12.3} for consistency.
    \end{itemize}
    \newpage
    \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_7_0.pdf}{1.7.0} (February 5, 2022)
    \begin{itemize}
        \item Added a new \hyperlink{subsection.12.2}{Section 12.2} to describe the \term{Farmers Market} to the \hyperlink{section.14}{Appendix}.
        \item Changed \term{Deposit} in the \hyperlink{subsection.14.11}{Glossary} for clarity. 
        \item Moved \term{Optimal State} in the \hyperlink{subsection.14.11}{Glossary} to reflect correct alphabetical ordering. 
        \item Added \term{Cancel}, \term{Farmers Market}, \term{Fill}, \term{Listing}, \term{Plot}, \term{Pod Line}, \term{Pod Listing}, and \term{Withdrawal} to the \hyperlink{subsection.14.11}{Glossary}. 
    \end{itemize}
        \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_8_0.pdf}{1.8.0} (March 10, 2022)
    \begin{itemize}
        \item Changed the fourth paragraph of \hyperlink{section.4}{Section 4} to reflect the update to the \term{Silo}, as amended by \href{https://bean.money/bip-12}{BIP-12}.\footnote{\href{https://bean.money/bip-12}{bean.money/bip-12}}
        \item Changed \hyperlink{section.6}{Section 6} to reflect the update to the \term{Silo}, as amended by \href{https://bean.money/bip-12}{BIP-12}. 
        \item Changed the third paragraph of \hyperlink{section.11}{Section 11} to reflect additional potential changes to the \term{Silo}. 
        \item Added  $c^{\lambda}$, $c_{t}^{\lambda}$, $g^{\lambda}(z^{\lambda})$, $k^{\lambda}$, $K_{t}^{\lambda}$, $l$, $\lambda$, $\Lambda$, $z^{\lambda}$ and $Z_i^{\lambda}$ to the \hyperlink{subsection.14.11}{Glossary}. 
        \item Changed $G$ to $\mu$, $\Lambda$ to $\phi$ and $\Lambda^{\text{Silo}}$ to $\phi^{\text{Silo}}$ in the \hyperlink{subsection.14.11}{Glossary}. 
        \item Removed $b_{\Omega}$, $c_{t}^{\bean}$, $c_{t}^{\Lambda}$, $k_{t}^{\bean}$, $k_{t}^{\Lambda}$, $l_{i}^{\Lambda}$, $\lambda^{\lambdabean}$, $\lambda^{\Lambda}$, ${\Lambda}_{\Omega}$, $z_{i}^{\bean}$, $z_{i}^{\Lambda}$, $z_{i}^{\Lambda:\bean}$ and $\Omega$ from the \hyperlink{subsection.14.11}{Glossary}.
    \end{itemize}
        \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_9_0.pdf}{1.9.0} (March 11, 2022)
    \begin{itemize}
        \item Updated \hyperref[fig 11]{Figure 11} and \hyperref[fig 12]{Figure 12} to reflect the new \term{Weather} changes, as amended by \href{https://bean.money/bip-13}{BIP-13}.\footnote{\href{https://bean.money/bip-13}{bean.money/bip-13}}
        \item Corrected a typo in the change history for Whitepaper Version \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_3_0.pdf}{1.3.0} in \hyperlink{subsection.12.3}{Section 12.3}.
    \end{itemize}
        \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_9_1.pdf}{1.9.1} (March 16, 2022)
    \begin{itemize}
        \item Corrected \hyperlink{subsubsection.8.4.8}{Section 8.4.8} to reflect the new \term{Weather} changes, as amended by \href{https://bean.money/bip-13}{BIP-13}.
        \item Updated Whitepaper Version History links for Versions 1.6.0, 1.7.0, and 1.8.0.
    \end{itemize}
        \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_9_2.pdf}{1.9.2} (April 1, 2022)
    \begin{itemize}
        \item Corrected a typo in the first paragraph of \hyperlink{subsection.6.2}{Section 6.2}.
        \item Updated the second paragraph of \hyperlink{subsection.6.2}{Section 6.2} to reflect the flash-loan-resistant nature of Bean-denominated-value.
        \item Corrected the formatting of $a^{\text{BIP}}$ and $A^{\text{BIP}}$.
        \item Corrected \hyperlink{subsubsection.6.5.5}{Section 6.5.5} to reflect the correct rate and duration that $a^q$ compounds.
        \item Updated the equation for $B$ in \hyperlink{subsubsection.8.4.5}{Section 8.4.5} to include $B^{\text{BIP}}$.
        \item Corrected \hyperlink{subsubsection.8.4.8}{Section 8.4.8} to reflect the \term{Weather} changes when $R^D$ equals $R^{D^{\text{lower}}}$, $R^{D^*}$ or $R^{D^{\text{upper}}}$.
        \item Added a new \hyperlink{subsection.12.2}{Section 12.2} to describe the \term{Silo} \term{Whitelist} to the \hyperlink{section.14}{Appendix}.
        \item Added a new \hyperlink{subsection.12.4}{Section 12.4} to describe \term{Fundraisers} to the \hyperlink{section.14}{Appendix}.
        \item Added $B^{\text{BIP}}$, BDV, $c^{\bean}$, $c^{\phi}$, $c^{\Phi}$, $E_{\Xi}$, $E_{\phi}$, $E_{\Psi}$, $\zeta^{\Phi}$, $g^{\bean}(z^{\bean})$, $g^{\phi}(z^{\phi})$, $g^{\Phi}(z^{\Phi})$, $g^{\text{3CRV}}(z^{\text{3CRV}})$, $k^{\bean}$, $k^{\phi}$, $k^{\Phi}$, $P^{\Phi}$, $P^{\text{3CRV}}$, $\Phi$, $\phi_{\overline{t}^{\bean}}$, $\phi_{\Xi}$, $\phi_{\Xi}^{\bean}$, $\Phi_{\Xi-1}$, $\Phi_{\Xi-1}^{\bean}$ and $\Phi_{\Xi-1}^{\text{3CRV}}$ to the \hyperlink{subsection.14.11}{Glossary}. 
        \item Corrected two typos in the \hyperlink{subsection.14.11}{Glossary}.
    \end{itemize}
         \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_9_3.pdf}{1.9.3} (April 3, 2022)
    \begin{itemize}
        \item Corrected typos in the eleventh paragraph of \hyperlink{subsubsection.8.4.5}{Section 8.4.5}, \hyperlink{subsection.12.2}{Section 12.2}, third paragraph of \hyperlink{subsection.12.4}{Section 12.4}, \hyperlink{subsection.14.11}{Glossary} and Whitepaper Version History changes for Version 1.1.0.
    \end{itemize}   
        \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_15_0.pdf}{1.15.0} (April 7, 2022)
    \begin{itemize}
        \item Moved to a new whitepaper versioning system such that Whitepaper Versions line up with \term{BIPs}. 
        \item Moved the definition of $B$ to \hyperlink{subsubsection.8.4.1}{Section 8.4.1} for consistency and clarity. 
        \item Updated \hyperlink{subsubsection.8.4.5}{Section 8.4.5} to reflect the new method to measure demand for \term{Soil}, as amended by \href{https://bean.money/bip-15}{BIP-15}.\footnote{\href{https://bean.money/bip-15}{bean.money/bip-15}}
        \item Added  $\Delta E_{t}^{u^{\text{first}}}$ and $E_{t}^{u^{\text{first}}}$ to the \hyperlink{subsection.14.11}{Glossary}. 
        \item Changed the definition of $\Delta E_{t}^{u}$ in the \hyperlink{subsection.14.11}{Glossary}. 
        \item Removed $\Delta E_{t}^{u^{\text{last}}}$, $\Delta R_{t-1}^S$, $\frac{\partial R^S}{\partial t}$, $\frac{\partial R^S}{\partial t}^{\text{upper}}$, $E_{t-1}^{u^{\text{first}}}$, $R^S$, $R^{S^{\text{min}}}$, $R_t^{S^{\text{end}}}$ and $R_t^{S^{\text{start}}}$ from the \hyperlink{subsection.14.11}{Glossary}.
        \item Added a comma for clarity in 18 instances in the Whitepaper Version History.
    \end{itemize}  
        \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk1_16_0.pdf}{1.16.0} (April 11, 2022)
    \begin{itemize}
        \item Modified Sections \hyperlink{subsubsection.12.2.3}{12.2.2} and \hyperlink{subsubsection.12.2.3}{12.2.3} for consistency.
        \item Added \hyperlink{subsubsection.12.2.4}{Section 12.2.4} to reflect the addition of $\alpha$ to the \term{Silo} \term{Whitelist}, as amended by \href{https://bean.money/bip-16}{BIP-16}.\footnote{\href{https://bean.money/bip-16}{bean.money/bip-16}} 
        \item Added  $\$^{\bean(\Phi)}$, $\$^{\text{LUSD}(\Omega))}$, $\alpha$, $c^{\alpha}$, $\zeta^{\Omega}$, $g^{\alpha}(z^{\alpha})$, $k^{\alpha}$, $P^{\alpha}$, $P^{\Omega}$, $\Phi^{A}$, $\Omega$, $\Omega^{A}$, $\Omega_{\Xi-1}$, $\Omega_{\Xi-1}^{\text{LUSD}}$ and $\Omega_{\Xi-1}^{\text{3CRV}}$ to the \hyperlink{subsection.14.11}{Glossary}. 
        \item Added the word ``liquidity'' for clarity in 6 instances in the \hyperlink{subsection.14.11}{Glossary}.
        \item Added the word ``v2'' for clarity in 3 instances in the \hyperlink{subsection.14.11}{Glossary}.
        \item Added the word ``Curve'' for clarity in 3 instances in the \hyperlink{subsection.14.11}{Glossary}.
        \item Moved the ordering of $P^{\Phi}$ and $P^{\text{3CRV}}$ in the \hyperlink{subsection.14.11}{Glossary} for consistency. 
    \end{itemize}  
        \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk2_0_0.pdf}{2.0.0} (August 6, 2022)
    \begin{itemize}
        \item Completely overhauled the whitepaper to reflect the state of Beanstalk after the \term{Replant}.
    \end{itemize}  
        \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk2_0_1.pdf}{2.0.1} (September 15, 2022)
    \begin{itemize}
        \item Changed \hyperlink{subsection.14.6}{Section 14.6} to reflect the update to the the calculation of $\Delta b_{\overline{t-1}}^{\Phi}$, as amended by \href{https://bean.money/ebip-2}{EBIP-2}.\footnote{\href{https://bean.money/ebip-2}{bean.money/ebip-2}}
        \item Updated \term{BIP} links throughout the whitepaper to the Beanstalk Governance Proposals GitHub Repository.\fref{github.com/BeanstalkFarms/Beanstalk-Governance-Proposals}
        \item Corrected eight instances of improper punctuation in the Whitepaper Version History.
    \end{itemize}  
        \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk2_1_0.pdf}{2.1.0} (October 5, 2022)
    \begin{itemize}
        \item Changed the last paragraph in \hyperlink{subsection.5.4}{Section 5.4} to reflect the addition of $\lambda$ $\rightarrow$ $\lambda$ \term{Converts}, as amended by \href{https://bean.money/bip-24}{BIP-24}.\footnote{\href{https://bean.money/bip-24}{bean.money/bip-24}}
        \item Corrected a typo in the last paragraph of \hyperlink{subsection.7.1}{Section 7.1} and the first paragraph of \hyperlink{subsubsection.7.3.1}{Section 7.3.1}.
        \item Added a new \hyperlink{subsubsection.14.4.1}{Section 14.4.1} to reflect the addition of $\lambda$ $\rightarrow$ $\lambda$ \term{Converts}, as amended by \href{https://bean.money/bip-24}{BIP-24}.
        \item Corrected the date of modification of Version 2.0.1 in the the Whitepaper Version History.
    \end{itemize}  
    \newpage
        \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk2_1_1.pdf}{2.1.1} (October 6, 2022)
    \begin{itemize}
        \item Corrected the BDV per token in Sections \hyperlink{subsubsection.14.5.2}{14.5.2}, \hyperlink{subsubsection.14.5.3}{14.5.3} and \hyperlink{subsubsection.14.5.4}{14.5.4}.
    \end{itemize}
        \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk2_2_0.pdf}{2.2.0} (November 11, 2022)
    \begin{itemize}
        \item Changed periods at the beginning of lists to colons for correctness.
        \item Removed \code{()} when referring to functions throughout the whitepaper.
        \item Changed Sections \hyperlink{paragraph.14.8.1.1}{14.8.1.1} and \hyperlink{paragraph.14.8.1.2}{14.8.1.2} to reflect the (1) addition of an input for \term{Pod Orders} and \term{Pod Listings} that specifies the minimum number of Pods that can be used to \term{Fill} them, as amended by \href{https://bean.money/ebip-3}{EBIP-3} and (2) upgrade to the price per \term{Pod} input for \term{Pod Orders} and \term{Pod Listings} to support a piecewise polynomial function that determines the price per \term{Pod} by its current place in the \term{Pod Line}, denominated in Beans, as amended by \href{https://bean.money/bip-29}{BIP-29}.\footnote{\href{https://bean.money/ebip-3}{bean.money/ebip-3}}$^{,}$\footnote{\href{https://bean.money/bip-29}{bean.money/bip-29}}
        \item Corrected a typo in the first paragraph of \hyperlink{paragraph.14.8.1.3}{Section 14.8.1.3}.
        \item Removed the future work item regarding support for arbitrary pricing functions in \term{Pod Orders} and \term{Pod Listings} in \hyperlink{paragraph.14.8.1.4}{Section 14.8.1.4}, as amended by \href{https://bean.money/bip-29}{BIP-29}.
        \item Updated intro to the \hyperlink{subsection.14.11}{Glossary} for clarity.
        \item Added $K^{\text{min}}$ to the \hyperlink{subsection.14.11}{Glossary}.
        \item Moved $\Phi$ in the \hyperlink{subsection.14.11}{Glossary}.
        \item Corrected a typo in the definition of $\Delta \mathfrak{R}^{\bean}$ in the \hyperlink{subsection.14.11}{Glossary}.
        \item Removed duplicate definitions of \term{Rinsable} and \term{Unfertilized Sprouts} from the \hyperlink{subsection.14.11}{Glossary}.
        \item Corrected a typo in the \hyperlink{subsection.14.12}{Whitepaper Version History} intro.
    \end{itemize}  
            \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk2_3_0.pdf}{2.3.0} (December 8, 2022)
    \begin{itemize}
        \item Updated the award for successfully calling the \code{sunrise} in \hyperlink{section.4}{Section 4}, as amended by \href{https://bean.money/bip-30}{BIP-30}.\footnote{\href{https://bean.money/bip-30}{bean.money/bip-30}}
        \item Changed Gnosis to Safe in \hyperlink{subsubsection.5.5.5}{Section 5.5.5}.
        \item Updated citation 29 with the new link for the \term{Beanstalk Community Multisig}.
        \item Updated \hyperlink{subsection.14.9}{Section 14.9} to reflect the addition of Pipeline \term{Pipeline} to \term{Depot}, as amended by \href{https://bean.money/bip-30}{BIP-30}.
        \item Updated \term{BIP} links throughout the whitepaper to \href{https://bean.money}{bean.money} links that redirect to an Arweave upload of the given \term{BIP}.
        \item Updated Snapshot proposal links throughout the whitepaper to \href{https://bean.money}{bean.money} links that redirect to an Arweave upload of the given proposal.
        \item Capitalized Whitepaper Version throughout the \hyperlink{subsection.14.12}{Whitepaper Version History} for consistency.
        \item Updated Whitepaper Version links in the \hyperlink{subsection.14.12}{Whitepaper Version History} to the Beanstalk Whitepaper GitHub Repository.\fref{github.com/BeanstalkFarms/Beanstalk-Whitepaper}
        \item Added citations for \href{https://bean.money/ebip-3}{EBIP-3} and \href{https://bean.money/bip-29}{BIP-29} in the \hyperlink{subsection.14.12}{Whitepaper Version History}.
        \item Corrected a citation formatting error under Version 2.0.1 in the \hyperlink{subsection.14.12}{Whitepaper Version History}.
        \item Corrected a typo under Version 1.16.0 in the \hyperlink{subsection.14.12}{Whitepaper Version History}.
    \end{itemize}  
    \newpage
        \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk2_4_0.pdf}{2.4.0} (July 3, 2023)
    \begin{itemize}
        \item Changed the \code{sunrise} function to the \code{gm} function throughout the whitepaper, as amended by \href{https://bean.money/bip-34}{BIP-34}.\footnote{\href{https://bean.money/bip-34}{bean.money/bip-34}}
        \item Updated the second paragraph of \hyperlink{section.4}{Section 4} to reflect that blocks on Ethereum are no longer mined after the Merge.
        \item Updated \hyperlink{section.4}{Section 4} to reflect the changes to the award for successfully calling the \code{gm} function, as amended by \href{https://bean.money/bip-34}{BIP-34}.
        \item Changed $E_t$ to $E_\Xi$ throughout the whitepaper for clarity.
        \item Corrected a typo in the second paragraph of \hyperlink{subsubsection.5.5.1}{Section 5.5.1}.
        \item Updated \hyperlink{subsubsection.5.5.1}{Section 5.5.1} to reflect that (1) a \term{Stalkholder's} vote is a function of their \term{Stalk} at the beginning of the \term{Voting Period} that still exists, (2) \term{Stalkholders} have the ability to delegate their vote to any other user, and (3) the submitter of a \term{BIP} must own more than $K_{\text{end}}^{\text{min}}$ percent of total \term{Stalk} at the end of the \term{Voting Period} in  order for the \term{BIP} to be able to pass, as amended by \href{https://bean.money/bip-35}{BIP-35}.\footnote{\href{https://bean.money/bip-35}{bean.money/bip-35}}
        \item Updated \hyperlink{subsubsection.5.5.2}{Section 5.5.2} to (1) improve clarity around when the \term{Voting Period} begins, (2) account for the \term{BIP} passing or failing based on the total outstanding \term{Stalk} at the beginning of the \term{Voting Period} that still exists, and (3) reintroduce the 24 hour period after the beginning and before the end of the \term{Voting Period} where a \term{BIP} cannot be passed via supermajority, as amended by \href{https://bean.money/bip-35}{BIP-35}.
        \item Updated the \term{BIP} inputs in the second paragraph of \hyperlink{subsubsection.5.5.4}{Section 5.5.4} to reflect the current state of off-chain governance.
        \item Updated \hyperlink{section.6}{Sections 6}, \hyperlink{subsection.6.1}{6.1} and \hyperlink{subsection.6.3}{6.3} to reflect the changes to the \term{Soil} supply and \term{Temperature} introduced by the \term{Morning}, as amended by \href{https://bean.money/bip-34}{BIP-34}.
        \item Updated \hyperlink{subsection.8.7}{Section 8.7} to reflect that (1) demand for \term{Soil} is now based on the number of \term{Sown} \Bean\ each \term{Season} rather than the change in \term{Soil} at the beginning and end of each \term{Season} and (2) Beanstalk considers demand for \term{Soil} increasing if $\Delta E_{t-1}^{u^{\text{first}}} < 600$, as amended by \href{https://bean.money/bip-34}{BIP-34}.
        \item Updated \hyperlink{subsection.8.11}{Sections 8.11} and \hyperlink{subsection.8.12}{8.12} and added \hyperlink{subsubsection.8.12.2}{Sections 8.12.1} and \hyperlink{subsubsection.8.12.2}{8.12.2} to reflect the changes in the \term{Soil} supply and \term{Temperature} introduced by the \term{Morning}, as amended by \href{https://bean.money/bip-34}{BIP-34}.
        \item Updated the \hyperlink{section.12}{Risk} section to include a citation for the Beanstalk DAO Disclosures.\fref{bean.money/disclosures}
        \item Replaced the Beanstalk audit report citation links in the \hyperlink{section.12}{Risk} section with the link to the Beanstalk Audits GitHub Repository.\fref{github.com/BeanstalkFarms/Beanstalk-Audits}
        \item Changed $\frac{\partial \Delta S}{\partial t}$ to $\frac{\partial u_t}{\partial t}$ in \hyperlink{section.13}{Future Work} for consistency.
        \item Updated the notation of percentage values in the \hyperlink{subsection.14.1}{Current Parameters} for clarity.
        \item Corrected $w_1$ to $h_1$ in \hyperlink{subsection.14.1}{Current Parameters}.
        \item Changed $\frac{\partial \Delta S}{\partial t}^{\text{lower}}$ and $\frac{\partial \Delta S}{\partial t}^{\text{upper}}$ to $\frac{\partial u_t}{\partial t}^{\text{lower}}$ and $\frac{\partial u_t}{\partial t}^{\text{upper}}$, respectively, in \hyperlink{subsection.14.1}{Current Parameters} for consistency.
        \item Added $K_{\text{end}}^{\text{min}}$, $Q$ and $\sigma$ to \hyperlink{subsection.14.1}{Current Parameters}.
        \item Removed $R^{S^{\text{min}}}$, $R^{S^{\text{max}}}$, and $\frac{\partial R^S}{\partial t}^{\text{upper}}$ from \hyperlink{subsection.14.1}{Current Parameters}.
        \item Updated \hyperlink{subsubsection.14.2.2}{Section 14.2.2} to reflect that the definitions of \hyperlink{ht3}{$\$^{\bean(\Phi)}_{\Xi-1}$}, \hyperlink{ht193}{$\Phi_{\Xi-1}^{\bean}$}, \hyperlink{ht194}{$\Phi_{\Xi-1}^{\text{3CRV}}$}, \hyperlink{ht136}{$P^{\text{3CRV}}$}, \hyperlink{ht190}{$\Phi^{A}$}, \hyperlink{ht140}{$P^{\Phi}$}, \hyperlink{ht96}{$\zeta^{\Phi}_{\Xi-1}$}, and \hyperlink{ht192}{$\Phi_{\Xi-1}$} were moved to \hyperlink{section.4}{Section 4}.
        \item Updated the intro of the \hyperlink{subsection.14.11}{Glossary} to include that the $q$ subscript is the current block of $t$.
        \item Added $h_t^{\text{max}}$, $h_{t_q}$, $K_{\text{end}}^{\text{min}}$, \term{Maximum Soil}, \term{Minimum Soil}, \term{Maximum Temperature}, $\varpi_\Xi$, $Q$, $q$, $\varrho$, $S_{t_q}^{\text{max}}$, $S_{t_q}^{\text{min}}$, $\sun_{\Xi}$, $\sigma$, $\varsigma$, $\vartheta$, $u_t$,  and $\frac{\partial u_t}{\partial t}$ to the \hyperlink{subsection.14.11}{Glossary}.
        \item Updated the definitions of $E_\Xi$, $S_t^{\text{end}}$ and $S_t^{\text{start}}$ in the \hyperlink{subsection.14.11}{Glossary}.
        \item Removed $E_{\Xi}^*$ and $S_t^{\text{min}}$ from the \hyperlink{subsection.14.11}{Glossary}.
        \item Added language to $a^q$, $E_q$ and $E_{\text{BIP}}$ in the \hyperlink{subsection.14.11}{Glossary} to clarify that they refer to \hyperlink{subsection.14.3}{Former Governance}.
        \item Corrected a typo under Version 2.0.1 in the \hyperlink{subsection.14.3}{Whitepaper Version History}. 
    \end{itemize}  
    \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk2_5_0.pdf}{2.5.0} (July 31, 2023)
    \begin{itemize}
        \item Added Beanstalk Farms as an author to the whitepaper.
        \item Updated \hyperlink{subsection.5.1}{Sections 5.1} and \hyperlink{subsection.5.4}{5.4} to reflect that \term{Grown} \term{Stalk} must now be \term{Mown} for each \hyperlink{ht126}{$\lambda$}, as amended by \href{https://bean.money/bip-36}{BIP-36}.\footnote{\href{https://bean.money/bip-36}{bean.money/bip-36}}
        \item Updated \hyperlink{subsection.5.3}{Section 5.3} to reflect the implementation of \term{Deposits} as ERC-1155 Standard tokens, as amended by \href{https://bean.money/bip-36}{BIP-36}.
        \item Updated \hyperref[fig 1]{Figure 1}, \hyperlink{subsection.5.3}{Sections 5.3}, \hyperlink{subsection.8.13}{8.13}, \hyperlink{subsection.11.6}{11.6}, \hyperlink{subsubsubsection.14.8.1.4}{14.8.1.4}, and \hyperlink{section.13}{Future Work} to reflect the removal of the \term{Withdrawal Freeze} and \term{Oversaturated}, as amended by \href{https://bean.money/bip-36}{BIP-36}.
        \item Updated \hyperlink{subsection.5.4}{Section 5.4} to reflect (1) that Beans minted to the \term{Silo} are distributed to \term{Stalkholders} and become \term{Earned} \Bean\ 10 blocks past the beginning of the \term{Season} in which they were minted, (2) the changes to the \term{Deposit} accounting system and (3) that \term{Stalk} is no longer lost due to rounding during \term{Conversions}, as amended by \href{https://bean.money/bip-36}{BIP-36}.
        \item Updated \hyperlink{subsubsection.5.5.5}{Section 5.5.5} and \hyperlink{section.13}{Future Work} to reflect the expectation that permissionless governance need not be reimplemented and that future \term{BIPs} will remove governance entirely. 
        \item Added the ERC-1155 Standard to the \hyperlink{section.12}{Risk} section.
        \item Removed $\xi$ from \hyperlink{subsection.14.1}{Current Parameters}.
        \item Corrected the formatting of \term{Stalk} and \term{Seeds} in \hyperlink{subsection.14.2}{Sections 14.2} and \hyperlink{subsection.14.5}{14.5}.
        \item Updated \hyperlink{subsubsection.14.2.3}{Sections 14.2.3} and \hyperlink{subsubsection.14.2.4}{14.2.4} to reflect that the \term{Seeds} per BDV for $\mathfrak{z}^{\bean}$ and $\mathfrak{z}^{\Phi}$ are 0, as amended by \href{https://bean.money/bip-36}{BIP-36}.
        \item Added \term{Deposit ID} to the \hyperlink{subsection.14.11}{Glossary}. 
        \item Updated the definitions of $D_{\gamma}$, $g_{t}^{\lambda}$ and $k_{t}^{\lambda}$ in the \hyperlink{subsection.14.11}{Glossary}.
        \item Changed $\varkappa$ to $\varkappa^{\lambda}$ in the \hyperlink{subsection.14.11}{Glossary}.
        \item Removed \term{Frozen}, \term{Oversaturated}, \term{Withdrawal Freeze} and \term{Withdrawn} assets from the \hyperlink{subsection.14.11}{Glossary}. 
        \item Corrected the formatting of \term{Minimum Soil} and $S_{t_q}^{\text{min}}$ in the \hyperlink{subsection.14.11}{Glossary}.
    \end{itemize}
    \item \href{https://github.com/BeanstalkFarms/Beanstalk-Whitepaper/blob/master/version-history/beanstalk2_6_0.pdf}{2.6.0} (October 16, 2023)
    \begin{itemize}
        \item Updated the email address for Beanstalk Farms.
        \item Updated \hyperlink{section.4}{Section 4} to reflect that the current price of ETH in Beans is calculated using the Multi Flow \term{Pump} on the BEAN:ETH \term{Well}, as amended by \href{https://bean.money/bip-37}{BIP-37}.\footnote{\href{https://bean.money/bip-37}{bean.money/bip-37}}
        \item Updated the citation for BIP-20\footnote{\href{https://bean.money/bip-20}{bean.money/bip-20}} in \hyperlink{subsubsection.7.3.3.}{Section 7.3.3}.
        \item Corrected a typo in the second paragraph of \hyperlink{section.8}{Section 8}.
        \item Corrected typos in the second and seventh paragraphs of \hyperlink{subsection.8.2}{Section 8.2}.
        \item Updated language in the third paragraph of \hyperlink{subsection.8.2}{Section 8.2} for accuracy.
        \item Updated the citation for WETH in \hyperlink{subsection.8.2}{Section 8.2}.
        \item Updated \hyperlink{subsection.8.2}{Section 8.2} to reflect the instances in which Beanstalk uses a Chainlink data feed as part of the price oracle, as amended by \href{https://bean.money/bip-37}{BIP-37}.
        \item Corrected a typo in the first paragraph of \hyperlink{subsection.8.13}{Section 8.13}.
        \item Updated \hyperlink{subsection.8.13}{Section 8.13} to reflect that (1) at the beginning of each \term{Season} during a \term{Flood}, Beanstalk returns the price of \Bean1 in each liquidity pool on the \term{Flood Whitelist} to its value peg by minting additional Beans and selling them directly in the pools, and (2) liquidity pools can be added to and removed from the \term{Flood Whitelist} via Beanstalk governance.
        \item Overhauled the \hyperlink{section.12}{Risk} section to reflect the current state of Beanstalk.
        \item Removed support of additional \term{Pipelines} from the \hyperlink{section.13}{Future Work} section.
        \item Added $\Theta^{\text{min}(\bean)}$ to the \hyperlink{subsection.14.1}{Current Parameters}.
        \item Reordered the \hyperlink{subsection.14.1}{Current Parameters} to be consistent with the updated  \hyperlink{subsection.14.11}{Glossary}.
        \item Updated \hyperlink{subsubsection.14.2.1}{Sections 14.2.1} and \hyperlink{subsubsection.14.2.2}{14.2.2} to reflect the change in \term{Seeds} per BDV for \Bean\ and $\Phi$ to 3 and 3.25, respectively, as amended by \href{https://bean.money/bip-37}{BIP-37}.
        \item Updated \hyperlink{subsubsection.14.2.2}{Section 14.2.2} to include the definitions of \hyperlink{ht3}{$\$^{\bean(\Phi)}_{\Xi-1}$}, \hyperlink{ht193}{$\Phi_{\Xi-1}^{\bean}$}, \hyperlink{ht194}{$\Phi_{\Xi-1}^{\text{3CRV}}$}, \hyperlink{ht136}{$P^{\text{3CRV}}$}, \hyperlink{ht190}{$\Phi^{A}$}, \hyperlink{ht140}{$P^{\Phi}$}, \hyperlink{ht96}{$\zeta^{\Phi}_{\Xi-1}$}, and \hyperlink{ht192}{$\Phi_{\Xi-1}$}, which were removed from \hyperlink{section.4}{Section 4}.
        \item Fixed typos in the BDV functions for \hyperlink{subsubsection.14.2.3}{Sections 14.2.3} and \hyperlink{subsubsection.14.2.3}{14.2.4}.
        \item Added \hyperlink{subsubsection.14.2.5}{Section 14.2.5} to reflect the addition of $\Theta$ to the \term{Deposit Whitelist}, as amended by \href{https://bean.money/bip-37}{BIP-37}.
        \item Fixed a typo in the fourth paragraph of \hyperlink{subsubsection.14.4.2}{Section 14.4.2} and under Conditions in \hyperlink{subsubsection.14.4.2}{Sections 14.4.2}, \hyperlink{subsubsection.14.4.3}{14.4.3}, \hyperlink{subsubsection.14.4.4}{14.4.4} and \hyperlink{subsubsection.14.4.5}{14.4.5}.
        \item Updated the \term{Convert} functions in \hyperlink{subsubsection.14.4.2}{Sections 14.4.2}, \hyperlink{subsubsection.14.4.3}{14.4.3}, \hyperlink{subsubsection.14.4.4}{14.4.4} and \hyperlink{subsubsection.14.4.5}{14.4.5} for accuracy.
        \item Added \hyperlink{subsubsection.14.4.6}{Sections 14.4.6} and \hyperlink{subsubsection.14.4.7}{Sections 14.4.7} to reflect the addition of \Bean\ $\rightarrow$ $\Theta$ and $\Theta$ $\rightarrow$ \Bean\ \term{Conversions} to the \term{Convert Whitelist}, as amended by \href{https://bean.money/bip-37}{BIP-37}.
        \item Amended \hyperlink{subsubsection.14.5.2}{Sections 14.5.2} and \hyperlink{subsubsection.14.5.3}{14.5.3} for clarity.
        \item Fixed a typo under \term{Seeds} per BDV in \hyperlink{subsubsection.14.5.3}{Section 14.5.3}. 
        \item Amended the intro to \hyperlink{subsection.14.6}{Section 14.6} for clarity.
        \item Fixed a typo and defined $B_{t-1}$ in \hyperlink{subsubsection.14.6.1}{Section 14.6.1}.
        \item Added \hyperlink{subsubsection.14.6.2}{Section 14.6.2} to reflect the addition of $\Theta$ to the \term{Oracle Whitelist}, as amended by \href{https://bean.money/bip-37}{BIP-37}.
        \item Renamed \hyperlink{subsection.14.7}{Section 14.7} to \term{Flood Whitelist} and updated the intro for clarity.
        \item Updated \hyperlink{subsubsection.14.9.2}{Section 14.9.2} to reflect the new Pipeline contract address used by \term{Depot}, as amended by \href{https://bean.money/bip-37}{BIP-37}.
        \item Overhauled the ordering of the \hyperlink{subsection.14.11}{Glossary} for readability.
        \item Added \term{Flood Whitelist}, TWA, $B_{t-1}$, $\Delta b_{\overline{t-1}}^{\Theta}$, $m_t$, $\frac{\partial \Theta}{\partial \bean}$, $\Theta^{\text{EMA}}_{\bean,\Game}$, $\Theta^{\text{EMA}}_{\text{ETH},\Game}$, $\Theta_{\Game}^{\text{ETH}}$, $\Theta^{\text{min}}$, $\Theta^{\text{min}(\bean)}$, $\Theta^{\text{SMA}}_{\bean,t_0,\Game}$, $\Theta^{\text{SMA}}_{\text{ETH},t_0,\Game}$, $\Theta^{*}$, $\Theta_{\Game}^{\bean}$, $\Theta_{\overline{t-1}}^{{\bean}^*}$, $\Theta^{\rightarrow}$, $\$^{\text{ETH}}$, $\$^{\text{ETH}(\nu)}$, $\$^{\text{ETH}(\tau)}$, $\$^{\text{ETH}(\chi)}$, $\Delta^{\$^{\text{ETH}(\nu \slash \chi)}}$, $\Delta^{\$^{\text{ETH}(\tau \slash \chi)}}$ and $\$^{\bean(\Theta)}$ to the \hyperlink{subsection.14.11}{Glossary}.
        \item Updated the definitions for \term{Flood}, $B^{\text{BIP}}$, $\Phi^{\text{min}}$ and $\Bean^{\text{min}}$ in the \hyperlink{subsection.14.11}{Glossary}.
        \item Removed $\kappa$ from the \hyperlink{subsection.14.11}{Glossary}.
    \end{itemize}
\end{itemize}
\end{document}